---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

Descriptive statistics for imputed data. first of all load in packages and custom functions. 
custom functions require imputed data to be in long format without the observed data included. 

```{r}
library(mice)
library(pander)
library(xtable)
library(dplyr)
library(gt)
library(glue)
library(miceadds)
library(swfscMisc)
library(imputools)
library(haven)
library(sjmisc)
library(Hmisc)
library(psych)
library(lavaan)
library(ggplot2)
library(ggpubr)
library(officer)
library(flextable)
library(ftExtra)
library(dummies)
library(tidyverse)

weighted_descriptives_imputed_datasets<- function (dataAll,variable) {
  variable=deparse(substitute(variable))
  imputed_datasets <- unique(dataAll$.imp)
  results <- data.frame(
    Mean = as.numeric(rep(0, length(imputed_datasets))),
    SD = as.numeric(rep(0, length(imputed_datasets))),
    lower=as.numeric(rep(0, length(imputed_datasets))),
    upper=as.numeric(rep(0, length(imputed_datasets))))
  results$Imputed <-  imputed_datasets
  for (i in 1:length(imputed_datasets)) {
    data <- dataAll[dataAll$.imp == imputed_datasets[i], ]
    results[i, "Mean"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[1]
    results[i, "SD"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[2]
    results[i, "lower"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[3]
    results[i, "upper"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[4]
  }
  return (results)
}


weighted_proportions_imputed_datasets<- function (dataAll,variable) {
  variable=deparse(substitute(variable))
  imputed_datasets <- unique(dataAll$.imp)
  results <- data.frame(
    Level1 = as.numeric(rep(0, length(imputed_datasets))),
    Level2 = as.numeric(rep(0, length(imputed_datasets))),
    Level3=as.numeric(rep(0, length(imputed_datasets))),
    Level4=as.numeric(rep(0, length(imputed_datasets))),
    Level5=as.numeric(rep(0, length(imputed_datasets))),
    Level6=as.numeric(rep(0, length(imputed_datasets))),
    Level7=as.numeric(rep(0, length(imputed_datasets))),
    Level8=as.numeric(rep(0, length(imputed_datasets))),
    Level9=as.numeric(rep(0, length(imputed_datasets))),
    Level10=as.numeric(rep(0, length(imputed_datasets))))
  results$Imputed <-  imputed_datasets
  for (i in 1:length(imputed_datasets)) {
    data <- dataAll[dataAll$.imp == imputed_datasets[i], ]
    results[i, "Level1"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[1]
    results[i, "Level2"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[2]
    results[i, "Level3"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[3]
    results[i, "Level4"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[4]
    results[i, "Level5"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[5]
    results[i, "Level6"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[6]
    results[i, "Level7"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[7]
    results[i, "Level8"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[8]
    results[i, "Level9"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[9]
    results[i, "Level10"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[10]
    
  }
  return (results)
}

load("~/Documents/PhD/updated MCS datasets/education-datasets/2022-01-04_vocabulary_education_imputedMAIN/2022-01-04_vocabulary_education_imputedMAIN.Rdata")
imputed_mcs2 = mi.res
load("~/Documents/PhD/updated MCS datasets/education-datasets/2022-01-05_vocabulary_education_imputedContinuousDescriptives/2022-01-05_vocabulary_education_imputedContinuousDescriptives.Rdata")
continuous_descriptives_imputed = mi.res

#convert imputed data to long format without observed data
long_format_mcs <- mice::complete(imputed_mcs2, "long", include=FALSE)
#redorder nvq and occupational status to have same order as whole cohort data - for occupational status and nvq
long_format_mcs$highest_nvq = factor(long_format_mcs$highest_nvq, levels = c("1", "2", "3", "4", "5", "0"))
long_format_mcs$occupational_status = factor(long_format_mcs$occupational_status, levels = c( "2", "3", "4", "1"))
long_format_descriptives <- mice::complete(continuous_descriptives_imputed , "long", include=TRUE)

```

for continuous outcome variable: need GCSE for england, wales and northern ireland (country !=3)
for N5 need scotland (country = 3)

```{r}
gcse= filter(long_format_descriptives, country !=3) %>% 
  select(!country)
n5 = filter(long_format_descriptives, country == 3) %>% 
  select(!country)

gcse_imputed = as.mids(gcse)
n5_imputed = as.mids(n5)

long_format_gcse = mice::complete(gcse_imputed, "long", include=FALSE)
long_format_n5 = mice::complete(n5_imputed, "long", include=FALSE)

```





run descritpives
```{r include = FALSE}

#numeric variables - means & SDs
#calculate descriptives across imputed datasets
vocabDescriptives = weighted_descriptives_imputed_datasets(long_format_mcs, age5_vocab)
caregiverVocabDescriptives = weighted_descriptives_imputed_datasets(long_format_mcs, caregiver_vocab)
gcseDescriptives = weighted_descriptives_imputed_datasets(long_format_gcse, average_grade)
n5Descriptives = weighted_descriptives_imputed_datasets(long_format_n5, average_grade_n5)

#combine across imputed datasets
combined_vocabDescriptives = round(combine_imputed_descriptives(vocabDescriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 
combined_caregiverVocabDescriptives = round(combine_imputed_descriptives(caregiverVocabDescriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1)
combined_gcseOutcomeDescriptives = round(combine_imputed_descriptives(gcseDescriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1)
combined_n5OutcomeDescriptives = round(combine_imputed_descriptives(n5Descriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1)

#categorical variables: proportions
sexProportions = weighted_proportions_imputed_datasets(long_format_mcs, sex) %>% 
  select(Level1:Level2) 
ethnicityProportions = weighted_proportions_imputed_datasets(long_format_mcs, ethnicity) %>% 
  select(Level1:Level6) 
ealProportions = weighted_proportions_imputed_datasets(long_format_mcs, EAL) %>% 
  select(Level1:Level3) 
countryProportions = weighted_proportions_imputed_datasets(long_format_mcs, country) %>% 
  select(Level1:Level4) 
nvqProportions = weighted_proportions_imputed_datasets(long_format_mcs, highest_nvq) %>% 
  select(Level1:Level6) 
incomeProportions = weighted_proportions_imputed_datasets(long_format_mcs, oecd_income) %>% 
  select(Level1:Level5) 
occupationProportions = weighted_proportions_imputed_datasets(long_format_mcs, occupational_status) %>% 
  select(Level1:Level4) 
wealthProportions = weighted_proportions_imputed_datasets(long_format_mcs, wealth_quintiles) %>% 
  select(Level1:Level5)  
imdProportions = weighted_proportions_imputed_datasets(long_format_mcs, imd) %>% 
  select(Level1:Level10)  
benchmarkProportions = weighted_proportions_imputed_datasets(long_format_mcs, benchmark_binary) %>% 
  select(Level1:Level2)  
 

sexCombined = round(combine_imputed_descriptives(sexProportions)*100, 2) %>% 
  slice_head(n=1) %>% 
  rename("Sex (Male)" = Level1,
         "Sex (Female)" = Level2) 
sexCombined = as.data.frame(t(sexCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ethnicityCombined = round(combine_imputed_descriptives(ethnicityProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename( "Ethnicity \n (White)" = Level1, 
          "Ethnicity \n (mixed)" = Level2,
          "Ethnicity \n (Indian)" = Level3, 
          "Ethnicity \n (Pakistani & Bangladeshi)" = Level4, 
          "Ethnicity \n (Black/ Black British)" = Level5, 
          "Ethnicity \n (other incl. Chinese)" = Level6)
ethnicityCombined = as.data.frame(t(ethnicityCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ealCombined = round(combine_imputed_descriptives(ealProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("EAL \n (English only)" = Level1, 
         "EAL \n (English and another language)" = Level2,
         "EAL \n (only another language)" = Level3)
ealCombined = as.data.frame(t(ealCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
countryCombined = round(combine_imputed_descriptives(countryProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Country \n (England)" = Level1, 
         "Country \n (Wales)" = Level2, 
         "Country \n (Scotland)" = Level3, 
         "Country \n (Northern Ireland)" = Level4)
countryCombined = as.data.frame(t(countryCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
nvqCombined = round(combine_imputed_descriptives(nvqProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Parent Education \n (NVQ1)" = Level1, 
         "Parent Education \n (NVQ2)"= Level2, 
         "Parent Education \n (NVQ3)" = Level3,
         "Parent Education \n (NVQ4)" = Level4,
         "Parent Education \n (NVQ5)" = Level5,
         "Parent Education \n (None of these/overseas qualifications)" = Level6)
nvqCombined = as.data.frame(t(nvqCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
incomeCombined = round(combine_imputed_descriptives(incomeProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Income Quintile 1" = Level1, 
         "Income Quintile 2" = Level2, 
         "Income Quintile 3" = Level3, 
         "Income Quintile 4" = Level4 , 
         "Income Quintile 5" = Level5)
incomeCombined = as.data.frame(t(incomeCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
occupationCombined = round(combine_imputed_descriptives(occupationProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Occupational Status \n (routine)" = Level1, 
         "Occupational Status \n (intermediate)" = Level2,
         "Occupational Status \n (higher managerial)" = Level3,
         "Occupational Status \n (unemployed)" = Level4)
occupationCombined = as.data.frame(t(occupationCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
wealthCombined = round(combine_imputed_descriptives(wealthProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Wealth Quintile 1" = Level1, 
         "Wealth Quintile 2" = Level2, 
         "Wealth Quintile 3" = Level3, 
         "Wealth Quintile 4" = Level4, 
         "Wealth Quintile 5" = Level5)
wealthCombined = as.data.frame(t(wealthCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
imdCombined = round(combine_imputed_descriptives(imdProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Relative Neighbourhood Deprivation \n (most deprived decile)" = Level1, 
         "Relative Neighbourhood Deprivation \n (10 - <20%)" = Level2, 
         "Relative Neighbourhood Deprivation \n (20 - <30%)" = Level3, 
         "Relative Neighbourhood Deprivation \n (30 - <40%)" = Level4, 
         "Relative Neighbourhood Deprivation \n (40 - <50%)" = Level5, 
         "Relative Neighbourhood Deprivation \n (50 - <60%)" = Level6, 
         "Relative Neighbourhood Deprivation \n (60 - <70%)" = Level7, 
         "Relative Neighbourhood Deprivation \n (70 - <80%)" = Level8, 
         "Relative Neighbourhood Deprivation \n (80 - <90%)"= Level9,
         "Relative Neighbourhood Deprivation \n (least deprived decile)" = Level10)
imdCombined = as.data.frame(t(imdCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
benchmarkCombined = round(combine_imputed_descriptives(benchmarkProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Core Subjects Grade ≥ 4: No" = Level1, 
        "Core Subjects Grade ≥ 4: Yes" = Level2)  
benchmarkCombined = as.data.frame(t(benchmarkCombined))%>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
        "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 

```

prepare for table.
will need to paste in 95%CIs with means and SDs and then put everything into one dataframe
```{r}
vocabDescriptives = combined_vocabDescriptives %>% add_column(paste0(combined_vocabDescriptives$Mean,"(±",combined_vocabDescriptives$SD,")", "\n", "[", combined_vocabDescriptives$lower, ";", combined_vocabDescriptives$upper,"]")) %>% 
  rename("cmVocab" = `paste0(...)`) %>% 
  add_column("Variable" = "Cohort Member Vocabulary \n (Naming Vocabulary Score)") %>% 
  select(Variable, cmVocab)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = cmVocab) 

caregiverVocabDescriptives = combined_caregiverVocabDescriptives %>% add_column(paste0(combined_caregiverVocabDescriptives$Mean,"(±",combined_caregiverVocabDescriptives$SD,")", "\n", "[", combined_caregiverVocabDescriptives$lower, ";", combined_caregiverVocabDescriptives$upper,"]")) %>% 
  rename("caregiverVocab" = `paste0(...)`) %>% 
  add_column("Variable" = "Caregiver Vocabulary \n (Word Activity Test Score)") %>% 
  select(Variable, caregiverVocab)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = caregiverVocab) 
   
gcse_outcomeDescriptives = combined_gcseOutcomeDescriptives  %>% add_column(paste0(combined_gcseOutcomeDescriptives$Mean,"(±",combined_gcseOutcomeDescriptives$SD,")", "\n", "[", combined_gcseOutcomeDescriptives$lower, ";", combined_gcseOutcomeDescriptives$upper,"]")) %>% 
  rename("gcseOutcome" = `paste0(...)`) %>% 
  add_column("Variable" = "Average GCSE grade \n (England, Wales & Northern Ireland)") %>% 
  select(Variable, gcseOutcome)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = gcseOutcome) 

n5_outcomeDescriptives = combined_n5OutcomeDescriptives  %>% add_column(paste0(combined_n5OutcomeDescriptives$Mean,"(±",combined_n5OutcomeDescriptives$SD,")", "\n", "[", combined_n5OutcomeDescriptives$lower, ";", combined_n5OutcomeDescriptives$upper,"]")) %>% 
  rename("n5Outcome" = `paste0(...)`) %>% 
  add_column("Variable" = "Average N5 grade \n (Scotland)") %>% 
  select(Variable, n5Outcome)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = n5Outcome) 


#put into one overall dataframe that can then  put into flex table

descriptivesTable = rbind(vocabDescriptives, caregiverVocabDescriptives, benchmarkCombined, gcse_outcomeDescriptives, n5_outcomeDescriptives,
                          sexCombined, ethnicityCombined, ealCombined, countryCombined,
                          nvqCombined, incomeCombined, wealthCombined, occupationCombined, imdCombined) %>% 
  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Cohort Member Education", .after = 3) %>% 
  add_row(Variable = "Demographics", .before = 9) %>% 
  add_row(Variable = "Socioeconomic Circumstances", .before = 25)
descriptivesTable [is.na(descriptivesTable )] <- " "
```


whole cohort descriptives , so can compare full cohort to analytic sample. 

```{r}
#read in full cohort data
mcs_cohort<-read.csv("cohort_data1.csv")
mcs_cohort[,1]<- NULL
#redorder nvq and occupational status variables 
mcs_cohort$highest_nvq = factor(mcs_cohort$highest_nvq, levels = c("1", "2", "3", "4", "5", "0"))
mcs_cohort$occupational_status = factor(mcs_cohort$occupational_status, levels = c( "2", "3", "4", "1"))
#get weighted proportions - need to remove NA values 
#sex
cohort_sex = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$sex),]$sex,
                         mcs_cohort[!is.na(mcs_cohort$sex),]$weight)*100, 2)
cohort_sex = as_tibble(cohort_sex) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Sex (Male)", "Sex (Female)"), .before = 1) 
  

#ethnicity
cohort_ethnicity = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$ethnicity),]$ethnicity,
                         mcs_cohort[!is.na(mcs_cohort$ethnicity),]$weight)*100,2)
cohort_ethnicity = as_tibble(cohort_ethnicity) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Ethnicity \n (White)",
                                   "Ethnicity \n (mixed)",
                                   "Ethnicity \n (Indian)",
                                   "Ethnicity \n (Pakistani & Bangladeshi)",
                                   "Ethnicity \n (Black/ Black British)",
                                   "Ethnicity \n (other incl. Chinese)"), .before = 1)


#EAL
cohort_eal = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$EAL),]$EAL,
                         mcs_cohort[!is.na(mcs_cohort$EAL),]$weight)*100,2)
cohort_eal = as_tibble(cohort_eal) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("EAL \n (English only)", 
                                   "EAL \n (English and another language)",
                                   "EAL \n (only another language)"), .before = 1)

#country
cohort_country = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$country),]$country,
                         mcs_cohort[!is.na(mcs_cohort$country),]$weight)*100,2)
cohort_country =  as_tibble(cohort_country) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Country \n (England)",
                                   "Country \n (Wales)", 
                                   "Country \n (Scotland)",
                                   "Country \n (Northern Ireland)"), .before = 1)

#NVQ
mcs_cohort$highest_nvq = as.factor(mcs_cohort$highest_nvq)
mcs_cohort$highest_nvq = relevel(mcs_cohort$highest_nvq, ref = "1")
cohort_nvq = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$highest_nvq),]$highest_nvq,
                         mcs_cohort[!is.na(mcs_cohort$highest_nvq),]$weight)*100,2)
cohort_nvq =  as_tibble(cohort_nvq) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Parent Education \n (NVQ1)",
                                   "Parent Education \n (NVQ2)",
                                   "Parent Education \n (NVQ3)",
                                   "Parent Education \n (NVQ4)", 
                                   "Parent Education \n (NVQ5)",
                                   "Parent Education \n (None of these/overseas qualifications)"), .before = 1)

#income
cohort_income = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$oecd_income),]$oecd_income,
                         mcs_cohort[!is.na(mcs_cohort$oecd_income),]$weight)*100,2)
cohort_income =  as_tibble(cohort_income) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Income Quintile 1",
                                   "Income Quintile 2", 
                                   "Income Quintile 3", 
                                   "Income Quintile 4", 
                                   "Income Quintile 5"), .before = 1)

#occupational status
mcs_cohort$occupational_status = as.factor(mcs_cohort$occupational_status)
mcs_cohort$occupational_status = relevel(mcs_cohort$occupational_status, ref = "2")
cohort_occupation = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$occupational_status),]$occupational_status,
                         mcs_cohort[!is.na(mcs_cohort$occupational_status),]$weight)*100,2)
cohort_occupation =  as_tibble(cohort_occupation) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Occupational Status \n (routine)",
                                   "Occupational Status \n (intermediate)",
                                   "Occupational Status \n (higher managerial)",
                                    "Occupational Status \n (unemployed)"), .before = 1)

#imd
cohort_imd = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$imd),]$imd,
                         mcs_cohort[!is.na(mcs_cohort$imd),]$weight)*100,2)
cohort_imd =  as_tibble(cohort_imd) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Relative Neighbourhood Deprivation \n (most deprived decile)", 
                                   "Relative Neighbourhood Deprivation \n (10 - <20%)",
                                   "Relative Neighbourhood Deprivation \n (20 - <30%)", 
                                   "Relative Neighbourhood Deprivation \n (30 - <40%)", 
                                   "Relative Neighbourhood Deprivation \n (40 - <50%)", 
                                   "Relative Neighbourhood Deprivation \n (50 - <60%)", 
                                   "Relative Neighbourhood Deprivation \n (60 - <70%)", 
                                   "Relative Neighbourhood Deprivation \n (70 - <80%)", 
                                   "Relative Neighbourhood Deprivation \n (80 - <90%)",
                                   "Relative Neighbourhood Deprivation \n (least deprived decile)"), .before = 1)

#benchmark reached 
mcs_cohort$benchmark_binary = as.factor(mcs_cohort$benchmark_binary)
cohort_benchmark = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$benchmark_binary),]$benchmark_binary,
                         mcs_cohort[!is.na(mcs_cohort$benchmark_binary),]$weight)*100,2)
cohort_benchmark =  as_tibble(cohort_benchmark) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Core Subjects Grade ≥ 4: No",
                                   "Core Subjects Grade ≥ 4: Yes"), .before = 1)

#means and SDs
#vocabulary
cohort_vocab = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$age5_vocab),]$age5_vocab,
                          mcs_cohort[!is.na(mcs_cohort$age5_vocab),]$weight),2)
cohort_vocab = as.data.frame(t(cohort_vocab)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_vocab = cohort_vocab %>% add_column(paste0(cohort_vocab$mean,"(±",cohort_vocab$sd,")", 
                                                  "\n", "[", cohort_vocab$lower, ";", cohort_vocab$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n (Naming Vocabulary Score)"), .before = 1)
  
  
  
  
#caregiver vocabulary
cohort_caregiverVocab = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$caregiver_vocab),]$caregiver_vocab,
                          mcs_cohort[!is.na(mcs_cohort$caregiver_vocab),]$weight),2)

cohort_caregiverVocab = as.data.frame(t(cohort_caregiverVocab)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_caregiverVocab = cohort_caregiverVocab %>% add_column(paste0(cohort_caregiverVocab$mean,"(±",cohort_caregiverVocab$sd,")", 
                                                  "\n", "[", cohort_caregiverVocab$lower, ";", cohort_caregiverVocab$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Caregiver Vocabulary \n (Word Activity Test Score)"), .before = 1)

#continuous education - GCSE for england, wales and NI
cohort_gcse = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$average_grade),]$average_grade,
                          mcs_cohort[!is.na(mcs_cohort$average_grade),]$weight),2)

cohort_gcse= as.data.frame(t(cohort_gcse)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_gcse = cohort_gcse %>% add_column(paste0(cohort_gcse$mean,"(±",cohort_gcse$sd,")", 
                                                  "\n", "[", cohort_gcse$lower, ";", cohort_gcse$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Average GCSE grade \n (England, Wales & Northern Ireland)"), .before = 1)


#continuous education - N5 for Scotland
cohort_n5 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$average_grade_n5),]$average_grade_n5,
                          mcs_cohort[!is.na(mcs_cohort$average_grade_n5),]$weight),2)

cohort_n5= as.data.frame(t(cohort_n5)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_n5 = cohort_n5 %>% add_column(paste0(cohort_n5$mean,"(±",cohort_n5$sd,")", 
                                                  "\n", "[", cohort_n5$lower, ";", cohort_n5$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Average N5 grade \n (Scotland)"), .before = 1)

descriptivesCohort = rbind(cohort_vocab, cohort_caregiverVocab, cohort_benchmark, cohort_gcse, cohort_n5,
                          cohort_sex, cohort_ethnicity, cohort_eal, cohort_country,
                          cohort_nvq, cohort_income, cohort_occupation, cohort_imd) %>% 
  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Cohort Member Education", .after = 3) %>% 
  add_row(Variable = "Demographics", .before = 9) %>% 
  add_row(Variable = "Socioeconomic Circumstances", .before = 25) %>% 
  add_row(Variable = "Wealth Quintile 1", .after = 36) %>% 
  add_row(Variable = "Wealth Quintile 2", .after = 37) %>% 
  add_row(Variable = "Wealth Quintile 3", .after = 38) %>% 
  add_row(Variable = "Wealth Quintile 4", .after = 39) %>% 
  add_row(Variable = "Wealth Quintile 5", .after = 40) 
    
descriptivesCohort [is.na(descriptivesCohort )] <- " "

```

combine analytical sample and full cohort descriptives
```{r}
fullDescriptives = cbind(descriptivesCohort, descriptivesTable)
names(fullDescriptives) = c("Variable" , "Full Cohort", "Var", "Analytical Sample")
fullDescriptives = fullDescriptives %>% select(!Var)

#put into table
#define border
my_border = border= fp_border(color="black", width=1)
full_descriptives <- fullDescriptives %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% #
  fontsize(size=10, part = "all") %>% #
  align(j=1, align="left", part="all") %>% 
  align(j=2:3, align="center", part="all") %>% 
  color(j=1:3, color="black", part="all") %>% 
  width(j=1, width=2) %>% 
  width(j=2:3, width=1.8) %>% 
  line_spacing(j=2:3, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:3, part="all", border=my_border) %>% 
  hline_bottom(j=1:3,part="body",  border=my_border) %>% 
  bold(j = 1, i = c(1,4,9,25), bold = TRUE) %>% 
  italic(j = 1, i = c(1,4,9,25), italic = TRUE) %>% 
  set_header_labels(Variable= "Variable", `Full Cohort` = "Whole Cohort \n (N= 19243)", 
                    `Analytical Sample` = "Analytical Sample (N=15,576)") %>% 
  add_header_row(values = c(" ", "Proportion (%) or \n Mean(±SD) [95% CIs]" ), colwidths = c(1, 2)) %>% 
  font(fontname = "Times New Roman", part="header") %>% 
  align(align="center", part="header") %>% 
  hline_top(j = 2:3, part = "all", border = my_border)  %>% 
  add_footer_lines(values = "Average GCSE grade refers to the average grade across English, Mathematics and Science subjects and was calculated post imputation on data from England, Wales and Northern Ireland.\nAverage N5 (National Five) grade refers to the average grade across English, Mathematics and Science subjects and was calculated post imputation on data from Scotland.\nWealth was derived post imputation and therefore we do not present the proportions for Wealth quintiles in the whole cohort, due to the high level of missing data among the wealth components.\nIn analyses, the average GCSE grade and average N5 grade were converted into z scores and combined into one variable pre-imputation.\nNote that descriptives for the whole cohort (N=19,243) do not indicate the level of missing data for these variables in the whole cohort.\nMissing data proportions for the analytical sample can be found in Figure S2.\nAnalytical sample descriptive statistics were calculated and pooled across 25 imputed datasets and are weighted to account for the sample design of the MCS2001 and attrition.") %>% 
  font(fontname = "Times New Roman", part = "footer") %>% 
  fontsize(size = 9, part = "footer") %>% 
  italic(part = "footer", italic = TRUE) %>% 
  align(align="left", part="footer") %>% 
  add_header_lines(values = c("Table 2: Descriptive Statistics for Analytical Sample (N = 15,576) and Whole MCS2001 Cohort (N=19,243)")) %>% 
  font(fontname = "Times New Roman", part = "header") %>% 
  fontsize(size = 12, part = "header") %>% 
  italic(part = "header", italic = TRUE)

  
  
  

 print(full_descriptives, preview = "docx") 


```


create flextable for descriptives
```{r}
#define border
my_border = border= fp_border(color="black", width=1)
descriptives_table <- descriptivesTable %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% #
  fontsize(size=10, part = "all") %>% #
  align(j=1, align="left", part="all") %>% 
  align(j=2, align="center", part="all") %>% 
  color(j=1:2, color="black", part="all") %>% 
  width(j=1, width=2) %>% 
  width(j=2, width=1.8) %>% 
  line_spacing(j=2, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:2, part="all", border=my_border) %>% 
  hline_bottom(j=1:2,part="body",  border=my_border) %>% 
  bold(j = 1, i = c(1,4,8,24), bold = TRUE) %>% 
  italic(j = 1, i = c(1,4,8,24), italic = TRUE) 
  
  

 print(descriptives_table, preview = "docx") 
```


