---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---


sensitivity check: complete cases for continuous outcome variable 
```{r}
library(mice)
library(pander)
library(xtable)
library(dplyr)
library(gt)
library(glue)
library(tidyverse)
library(miceadds)
library(swfscMisc)
library(imputools)
library(haven)
library(sjmisc)
library(Hmisc)
library(psych)
library(lavaan)
library(ggplot2)
library(ggpubr)
library(officer)
library(flextable)
library(ftExtra)
library(ggeffects)
library(gtools)

#this will take a float (e.g. a p value) and return a string with 3 digits and no leading 0

bv <- function(val) {
  return(sub("^(-?)0.", "\\1.", sprintf("%.2f", val)))
}

#if the number is less than .001, it will give <.001. 
pv1 <- function(val) {
  return(paste("=", sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
}

load("~/Documents/PhD/updated MCS datasets/education-datasets/2021-12-17_vocabulary_education_imputed_continuousCompleteCases/2021-12-17_vocabulary_education_imputed_continuousCompleteCases.Rdata")
imputed_mcs2 = mi.res

```

RQ1 & 2 - DOES VOCAB PREDICT EDUCATIONAL ATTAINMENT?


Continuous outcome variable####
does vocabulary predict level of achievement in core subjects regardless of pass/ fail? 

```{r}
#unadjusted relationship

continuous_unadjusted = with(imputed_mcs2, lm(standardised_core_subjects ~ age5_standardised, weights = weight))

continuous_unadjusted_results = round(summary(pool(continuous_unadjusted), conf.int = TRUE),2)

#adjusted relationship 
continuous_model1 = with(imputed_mcs2, lm(standardised_core_subjects ~ sex + ethnicity + EAL + country +
                                         highest_nvq + oecd_income + occupational_status + wealth_quintiles + imd, 
                                       weights = weight))

continuous_model2 = with(imputed_mcs2, lm(standardised_core_subjects ~ sex + ethnicity + EAL + country +
                                         highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                         imd + caregiver_vocabStandardised, 
                                        weights = weight))

continuous_model3 = with(imputed_mcs2, lm(standardised_core_subjects ~ sex + ethnicity + EAL + country +
                                         highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                         imd + caregiver_vocabStandardised + age5_standardised, 
                                        weights = weight))

continuous_model1Results = summary(pool(continuous_model1), conf.int = TRUE)
continuous_model2Results = summary(pool(continuous_model2), conf.int = TRUE)
continuous_model3Results = summary(pool(continuous_model3), conf.int = TRUE)

round(pool.r.squared(continuous_unadjusted),4)*100
cont_model1R2 = as.data.frame(round(pool.r.squared(continuous_model1),4)*100)
cont_model2R2 = as.data.frame(round(pool.r.squared(continuous_model2),4)*100)
cont_model3R2 = as.data.frame(round(pool.r.squared(continuous_model3),4)*100)

```

does vocabulary predict level of achievement in core subjects above and beyond SEC/caregiver vocab factors?

```{r}
#compare sociodemographics model to no predictors
#create null model 
null_continuousModel =  with(imputed_mcs2, lm(standardised_core_subjects ~ 1, weights = weight))
D1(continuous_model1, null_continuousModel)
#compare model with only sociodemographic factors to a model with caregiver vocab
D1(continuous_model2, continuous_model1) #check if need to use a specific method ?
#compare model with all confounders to model with vocab
D1(continuous_model3, continuous_model2) 

```

gather relevant information for table

```{r}

#contunous outcome ####
#model 1 for continuous outcome
continuous_model1Results$estimate = bv(continuous_model1Results$estimate) #no leading 0 
continuous_model1Results$`2.5 %` = bv(continuous_model1Results$`2.5 %`)
continuous_model1Results$`97.5 %` = bv(continuous_model1Results$`97.5 %`)
continuous_model1Results$p.value1= ifelse(continuous_model1Results$p.value< .001, "<.001" , pv1(continuous_model1Results$p.value))
continuous_model1Results$coefficient = paste0(continuous_model1Results$estimate, "[", continuous_model1Results$`2.5 %`, ";", continuous_model1Results$`97.5 %`, "]")
continuous_model1Results$stars = add.significance.stars(continuous_model1Results$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model1Results$p1 = paste0(continuous_model1Results$p.value1, "")
continuous_model1Results$p = paste0("p", continuous_model1Results$p1)
continuous_model1Results$new_coef = paste0(continuous_model1Results$coefficient, continuous_model1Results$stars)  #combine coefficients and stars into column.

#model 2 for continuous outcome
continuous_model2Results$estimate = bv(continuous_model2Results$estimate) #no leading 0 
continuous_model2Results$`2.5 %` = bv(continuous_model2Results$`2.5 %`)
continuous_model2Results$`97.5 %` = bv(continuous_model2Results$`97.5 %`)
continuous_model2Results$p.value1= ifelse(continuous_model2Results$p.value< .001, "<.001" , pv1(continuous_model2Results$p.value))
continuous_model2Results$coefficient = paste0(continuous_model2Results$estimate, "[", continuous_model2Results$`2.5 %`, ";", continuous_model2Results$`97.5 %`, "]")
continuous_model2Results$stars = add.significance.stars(continuous_model2Results$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model2Results$p1 = paste0(continuous_model2Results$p.value1, "")
continuous_model2Results$p = paste0("p", continuous_model2Results$p1)
continuous_model2Results$new_coef = paste0(continuous_model2Results$coefficient, continuous_model2Results$stars)  #combine coefficients and stars into column.


#model 3 for continuous outcome
continuous_model3Results$estimate = bv(continuous_model3Results$estimate) #no leading 0 
continuous_model3Results$`2.5 %` = bv(continuous_model3Results$`2.5 %`)
continuous_model3Results$`97.5 %` = bv(continuous_model3Results$`97.5 %`)
continuous_model3Results$p.value1= ifelse(continuous_model3Results$p.value< .001, "<.001" , pv1(continuous_model3Results$p.value))
continuous_model3Results$coefficient = paste0(continuous_model3Results$estimate, "[", continuous_model3Results$`2.5 %`, ";", continuous_model3Results$`97.5 %`, "]")
continuous_model3Results$stars = add.significance.stars(continuous_model3Results$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model3Results$p1 = paste0(continuous_model3Results$p.value1, "")
continuous_model3Results$p = paste0("p", continuous_model3Results$p1)
continuous_model3Results$new_coef = paste0(continuous_model3Results$coefficient, continuous_model3Results$stars)  #combine coefficients and stars into column.



#get coefficients and 95% CIs for table: linear regression
continuous_model1Results = continuous_model1Results %>% select(term, new_coef, p)
continuous_model2Results = continuous_model2Results %>% select(term, new_coef, p)
continuous_model3Results = continuous_model3Results %>% select(term, new_coef, p)

continuous_model1Results$model1_b <- paste0(continuous_model1Results$new_coef,"\n", continuous_model1Results$p) 
continuous_model2Results$model2_b <- paste0(continuous_model2Results$new_coef,"\n", continuous_model2Results$p) 
continuous_model3Results$model3_b <- paste0(continuous_model3Results$new_coef,"\n", continuous_model3Results$p) 

continuous_model1Results = continuous_model1Results %>% select(term, model1_b)
continuous_model2Results = continuous_model2Results %>% select(term, model2_b)
continuous_model3Results = continuous_model3Results %>% select(term, model3_b)


#add column to make it the same length for all 3 models - needs to be as long as model 3 
continuous_model1Results = continuous_model1Results %>% add_row(term = "caregiver_vocabStandardised") %>% 
  add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model1_b =paste0(cont_model1R2$est,"[", cont_model1R2$`lo 95`, ";", cont_model1R2$`hi 95`,"]"), .after = 39)
continuous_model2Results = continuous_model2Results %>% add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model2_b =paste0(cont_model2R2$est,"[", cont_model2R2$`lo 95`, ";", cont_model2R2$`hi 95`,"]"), .after = 39)
continuous_model3Results = continuous_model3Results %>% 
  add_row(term = "R2", model3_b =paste0(cont_model3R2$est,"[", cont_model3R2$`lo 95`, ";", cont_model3R2$`hi 95`,"]"), .after = 39)

continuous_outcomeResults = cbind(continuous_model1Results, continuous_model2Results, continuous_model3Results)
continuous_outcomeResults = continuous_outcomeResults %>% select(!3 & !5)

continuous_outcomeResults = continuous_outcomeResults %>% add_row(term = "Sociodemographic confounders", .after = 1) %>% 
  add_row(term = "Caregiver vocabulary", .before = 39) %>% 
  add_row(term = "Cohort member vocabulary", .before  = 41)


regression_resultsTable = continuous_outcomeResults
regression_resultsTable [is.na(regression_resultsTable )] <- "  "
regression_resultsTable = regression_resultsTable %>% 
  slice(-(1)) %>% #remove intercept row
  add_row(term = "sex1", .after = 1) %>% #add in reference categories for factor variables
  add_row(term = "ethnicity1", .after = 3) %>% 
  add_row(term = "EAL1", .after = 9) %>% 
  add_row(term = "country1", .after =  12) %>% 
  add_row(term = "highest_nvq1", .after = 16) %>% 
  add_row(term = "oecd_income1", .after = 22) %>% 
  add_row(term = "occupational_status2", .after = 27) %>% 
  add_row(term = "wealth_quintiles1", .after = 31) %>% 
  add_row(term = "imd1", .after = 36 )
regression_resultsTable [is.na(regression_resultsTable )] <- "REFERENCE"
  
#rename variables column 

regression_resultsTable$term <- c("Sociodemographic confounders", "Sex (male)", "Sex (female)", 
                                  "Ethnicity \n (White)", "Ethnicity \n (mixed)", "Ethnicity \n (Indian)", "Ethnicity \n (Pakistani & Bangladeshi)", "Ethnicity \n (Black/ Black British)", "Ethnicity \n (other incl. Chinese)", 
                                  "EAL \n (English only)", "EAL \n (English and another language)", "EAL \n (only another language)", 
                                  "Country \n (England)", "Country \n (Wales)", "Country \n (Scotland)", "Country \n (Northern Ireland)",
                                  "Parent Education \n (NVQ1)", "Parent Education \n (None of these/overseas qualifications)", "Parent Education \n (NVQ2)", "Parent Education \n (NVQ3)", "Parent Education \n (NVQ4)", "Parent Education \n (NVQ5)", 
                           "Income Quintile 1", "Income Quintile 2", "Income Quintile 3", "Income Quintile 4", "Income Quintile 5", 
                           "Occupational Status \n (routine)", "Occupational Status \n (unemployed)", "Occupational Status \n (intermediate)", "Occupational Status \n (higher managerial)",  
                           "Wealth Quintile 1", "Wealth Quintile 2", "Wealth Quintile 3", "Wealth Quintile 4", "Wealth Quintile 5",
                          "Relative Neighbourhood \n Deprivation \n (most deprived decile)", "Relative Neighbourhood \n Deprivation \n (10 - <20%)", "Relative Neighbourhood \n Deprivation \n (20 - <30%)", "Relative Neighbourhood \n Deprivation \n (30 - <40%)", "Relative Neighbourhood \n Deprivation \n (40 - <50%)", "Relative Neighbourhood \n Deprivation \n (50 - <60%)", "Relative Neighbourhood \n Deprivation \n (60 - <70%)", "Relative Neighbourhood \n  Deprivation \n (70 - <80%)", "Relative Neighbourhood \n Deprivation \n (80 - <90%)", "Relative Neighbourhood \n Deprivation \n (least deprived decile)", "Caregiver Vocabulary", "Caregiver Vocabulary \n (Word Activity Test Score)", "Cohort Member Vocabulary", "Cohort Member Vocabulary \n (Naming Vocabulary Score)", "R2 (%)")

```



Create results table using flextable package - this can be exported straight into word. 

```{r}
#define border
my_border = border= fp_border(color="black", width=1)
results_continuousCC <- regression_resultsTable %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% #
  fontsize(size=10, part = "all") %>% #
  align(j=1, align="left", part="all") %>% 
  align(j=2:4, align="center", part="all") %>% 
  color(j=1:4, color="black", part="all") %>% 
  width(j=1, width=1) %>% 
  width(j=2:4, width=1.4) %>% 
  line_spacing(j=2:4, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:4, part="all", border=my_border) %>% 
  hline_bottom(j=1:4,part="body",  border=my_border) %>% 
  set_header_labels(term= "Variable",
                    model1_b="Model 1", model2_b = "Model 2", model3_b = "Model 3") %>% 
 add_header_row(values = c(" ",  "Continuous Outcome (B[95% CIs]"), colwidths = c(1, 3)) %>% 
  font(fontname = "Times New Roman", part="header") %>% 
  align(align="center", part="header") %>% 
  hline_top(j = 2:4, part = "all", border = my_border) %>% 
  bold(j = 1, i = c(1,47, 49), bold = TRUE) %>% 
  italic(j = 1, i = c(1,47, 49), italic = TRUE) 

```

