---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r}
library(mice)
library(pander)
library(xtable)
library(dplyr)
library(gt)
library(glue)
library(tidyverse)
library(miceadds)
library(swfscMisc)
library(imputools)
library(haven)
library(sjmisc)
library(Hmisc)
library(psych)
library(lavaan)
library(ggplot2)
library(ggpubr)
library(officer)
library(flextable)
library(ftExtra)
library(ggeffects)
library(gtools)

#this will take a float (e.g. a p value) and return a string with 3 digits and no leading 0

bv <- function(val) {
  return(sub("^(-?)0.", "\\1.", sprintf("%.2f", val)))
}

#if the number is less than .001, it will give <.001. 
pv1 <- function(val) {
  return(paste("=", sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
}

load("~/Documents/PhD/updated MCS datasets/education-datasets/2021-12-20_vocabulary_education_exploratoryAnalysis_imputedData/2021-12-20_vocabulary_education_exploratoryAnalysis_imputedData.Rdata")
imputed_mcs2 = mi.res


```

#english, maths and science average grades considered as separate outcomes - exploratory analysis to see if vocabulary differentially predicts these subjects

#english 
```{r}
#unadjusted relationship

continuous_unadjustedEnglish = with(imputed_mcs2, lm(standardised_english ~ age5_standardised, weights = weight))

continuous_unadjusted_resultsEnglish = round(summary(pool(continuous_unadjustedEnglish), conf.int = TRUE),2)

#adjusted relationship 
continuous_model1English= with(imputed_mcs2, lm(standardised_english ~ sex + ethnicity + EAL + country +
                                         highest_nvq + oecd_income + occupational_status + wealth_quintiles + imd, 
                                       weights = weight))

continuous_model2English = with(imputed_mcs2, lm(standardised_english ~ sex + ethnicity + EAL + country +
                                         highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                         imd + caregiver_vocabStandardised, 
                                        weights = weight))

continuous_model3English = with(imputed_mcs2, lm(standardised_english ~ sex + ethnicity + EAL + country +
                                         highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                         imd + caregiver_vocabStandardised + age5_standardised, 
                                        weights = weight))

continuous_model1ResultsEnglish = summary(pool(continuous_model1English), conf.int = TRUE)
continuous_model2ResultsEnglish = summary(pool(continuous_model2English), conf.int = TRUE)
continuous_model3ResultsEnglish = summary(pool(continuous_model3English), conf.int = TRUE)

round(pool.r.squared(continuous_unadjustedEnglish),4)*100
cont_model1R2English = as.data.frame(round(pool.r.squared(continuous_model1English),4)*100)
cont_model2R2English = as.data.frame(round(pool.r.squared(continuous_model2English),4)*100)
cont_model3R2English = as.data.frame(round(pool.r.squared(continuous_model3English),4)*100)
```

2b. does vocabulary predict level of achievement in core subjects above and beyond SEC/caregiver vocab factors?

```{r}
#compare sociodemographics model to no predictors
#create null model 
null_continuousModelEnglish =  with(imputed_mcs2, lm(standardised_english ~ 1, weights = weight))
D1(continuous_model1English, null_continuousModelEnglish)
#compare model with only sociodemographic factors to a model with caregiver vocab
D1(continuous_model2English, continuous_model1English) #check if need to use a specific method ?
#compare model with all confounders to model with vocab
D1(continuous_model3English, continuous_model2English) 
```

maths
```{r}
continuous_unadjustedMaths = with(imputed_mcs2, lm(standardised_maths ~ age5_standardised, weights = weight))

continuous_unadjusted_resultsMaths = round(summary(pool(continuous_unadjustedMaths), conf.int = TRUE),2)

#adjusted relationship 
continuous_model1Maths= with(imputed_mcs2, lm(standardised_maths ~ sex + ethnicity + EAL + country +
                                                  highest_nvq + oecd_income + occupational_status + wealth_quintiles + imd, 
                                                weights = weight))

continuous_model2Maths = with(imputed_mcs2, lm(standardised_maths ~ sex + ethnicity + EAL + country +
                                                   highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                                   imd + caregiver_vocabStandardised, 
                                                 weights = weight))

continuous_model3Maths = with(imputed_mcs2, lm(standardised_maths ~ sex + ethnicity + EAL + country +
                                                   highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                                   imd + caregiver_vocabStandardised + age5_standardised, 
                                                 weights = weight))

continuous_model1ResultsMaths = summary(pool(continuous_model1Maths), conf.int = TRUE)
continuous_model2ResultsMaths = summary(pool(continuous_model2Maths), conf.int = TRUE)
continuous_model3ResultsMaths = summary(pool(continuous_model3Maths), conf.int = TRUE)

round(pool.r.squared(continuous_unadjustedMaths),4)*100
cont_model1R2Maths = as.data.frame(round(pool.r.squared(continuous_model1Maths),4)*100)
cont_model2R2Maths = as.data.frame(round(pool.r.squared(continuous_model2Maths),4)*100)
cont_model3R2Maths = as.data.frame(round(pool.r.squared(continuous_model3Maths),4)*100)
```

2b. does vocabulary predict level of achievement in core subjects above and beyond SEC/caregiver vocab factors?
  
```{r}
#compare sociodemographics model to no predictors
#create null model 
null_continuousModelMaths =  with(imputed_mcs2, lm(standardised_maths ~ 1, weights = weight))
D1(continuous_model1Maths, null_continuousModelMaths)
#compare model with only sociodemographic factors to a model with caregiver vocab
D1(continuous_model2Maths, continuous_model1Maths) #check if need to use a specific method ?
#compare model with all confounders to model with vocab
D1(continuous_model3Maths, continuous_model2Maths) 
```

science 
```{r}
continuous_unadjustedScience = with(imputed_mcs2, lm(standardised_science ~ age5_standardised, weights = weight))

continuous_unadjusted_resultsScience = round(summary(pool(continuous_unadjustedScience), conf.int = TRUE),2)

#adjusted relationship 
continuous_model1Science= with(imputed_mcs2, lm(standardised_science ~ sex + ethnicity + EAL + country +
                                                  highest_nvq + oecd_income + occupational_status + wealth_quintiles + imd, 
                                                weights = weight))

continuous_model2Science = with(imputed_mcs2, lm(standardised_science ~ sex + ethnicity + EAL + country +
                                                   highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                                   imd + caregiver_vocabStandardised, 
                                                 weights = weight))

continuous_model3Science = with(imputed_mcs2, lm(standardised_science ~ sex + ethnicity + EAL + country +
                                                   highest_nvq + oecd_income + occupational_status + wealth_quintiles + 
                                                   imd + caregiver_vocabStandardised + age5_standardised, 
                                                 weights = weight))

continuous_model1ResultsScience = summary(pool(continuous_model1Science), conf.int = TRUE)
continuous_model2ResultsScience = summary(pool(continuous_model2Science), conf.int = TRUE)
continuous_model3ResultsScience = summary(pool(continuous_model3Science), conf.int = TRUE)

round(pool.r.squared(continuous_unadjustedScience),4)*100
cont_model1R2Science = as.data.frame(round(pool.r.squared(continuous_model1Science),4)*100)
cont_model2R2Science = as.data.frame(round(pool.r.squared(continuous_model2Science),4)*100)
cont_model3R2Science = as.data.frame(round(pool.r.squared(continuous_model3Science),4)*100)
```

2b. does vocabulary predict level of achievement in core subjects above and beyond SEC/caregiver vocab factors?
  
```{r}
#compare sociodemographics model to no predictors
#create null model 
null_continuousModelScience =  with(imputed_mcs2, lm(standardised_science ~ 1, weights = weight))
D1(continuous_model1Science, null_continuousModelScience)
#compare model with only sociodemographic factors to a model with caregiver vocab
D1(continuous_model2Science, continuous_model1Science) #check if need to use a specific method ?
#compare model with all confounders to model with vocab
D1(continuous_model3Science, continuous_model2Science) 

```

results table 

get data for tables 
```{r}
#english 
#model 1 for continuous outcome
continuous_model1ResultsEnglish$estimate = bv(continuous_model1ResultsEnglish$estimate) #no leading 0 
continuous_model1ResultsEnglish$`2.5 %` = bv(continuous_model1ResultsEnglish$`2.5 %`)
continuous_model1ResultsEnglish$`97.5 %` = bv(continuous_model1ResultsEnglish$`97.5 %`)
continuous_model1ResultsEnglish$p.value1= ifelse(continuous_model1ResultsEnglish$p.value< .001, "<.001" , pv1(continuous_model1ResultsEnglish$p.value))
continuous_model1ResultsEnglish$coefficient = paste0(continuous_model1ResultsEnglish$estimate, "[", continuous_model1ResultsEnglish$`2.5 %`, ";", continuous_model1ResultsEnglish$`97.5 %`, "]")
continuous_model1ResultsEnglish$stars = add.significance.stars(continuous_model1ResultsEnglish$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model1ResultsEnglish$p1 = paste0(continuous_model1ResultsEnglish$p.value1, "")
continuous_model1ResultsEnglish$p = paste0("p", continuous_model1ResultsEnglish$p1)
continuous_model1ResultsEnglish$new_coef = paste0(continuous_model1ResultsEnglish$coefficient, continuous_model1ResultsEnglish$stars)  #combine coefficients and stars into column.

#model 2 for continuous outcome
continuous_model2ResultsEnglish$estimate = bv(continuous_model2ResultsEnglish$estimate) #no leading 0 
continuous_model2ResultsEnglish$`2.5 %` = bv(continuous_model2ResultsEnglish$`2.5 %`)
continuous_model2ResultsEnglish$`97.5 %` = bv(continuous_model2ResultsEnglish$`97.5 %`)
continuous_model2ResultsEnglish$p.value1= ifelse(continuous_model2ResultsEnglish$p.value< .001, "<.001" , pv1(continuous_model2ResultsEnglish$p.value))
continuous_model2ResultsEnglish$coefficient = paste0(continuous_model2ResultsEnglish$estimate, "[", continuous_model2ResultsEnglish$`2.5 %`, ";", continuous_model2ResultsEnglish$`97.5 %`, "]")
continuous_model2ResultsEnglish$stars = add.significance.stars(continuous_model2ResultsEnglish$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model2ResultsEnglish$p1 = paste0(continuous_model2ResultsEnglish$p.value1, "")
continuous_model2ResultsEnglish$p = paste0("p", continuous_model2ResultsEnglish$p1)
continuous_model2ResultsEnglish$new_coef = paste0(continuous_model2ResultsEnglish$coefficient, continuous_model2ResultsEnglish$stars)  #combine coefficients and stars into column.


#model 3 for continuous outcome
continuous_model3ResultsEnglish$estimate = bv(continuous_model3ResultsEnglish$estimate) #no leading 0 
continuous_model3ResultsEnglish$`2.5 %` = bv(continuous_model3ResultsEnglish$`2.5 %`)
continuous_model3ResultsEnglish$`97.5 %` = bv(continuous_model3ResultsEnglish$`97.5 %`)
continuous_model3ResultsEnglish$p.value1= ifelse(continuous_model3ResultsEnglish$p.value< .001, "<.001" , pv1(continuous_model3ResultsEnglish$p.value))
continuous_model3ResultsEnglish$coefficient = paste0(continuous_model3ResultsEnglish$estimate, "[", continuous_model3ResultsEnglish$`2.5 %`, ";", continuous_model3ResultsEnglish$`97.5 %`, "]")
continuous_model3ResultsEnglish$stars = add.significance.stars(continuous_model3ResultsEnglish$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model3ResultsEnglish$p1 = paste0(continuous_model3ResultsEnglish$p.value1, "")
continuous_model3ResultsEnglish$p = paste0("p", continuous_model3ResultsEnglish$p1)
continuous_model3ResultsEnglish$new_coef = paste0(continuous_model3ResultsEnglish$coefficient, continuous_model3ResultsEnglish$stars)  #combine coefficients and stars into column.

#maths
#model 1 for continuous outcome
continuous_model1ResultsMaths$estimate = bv(continuous_model1ResultsMaths$estimate) #no leading 0 
continuous_model1ResultsMaths$`2.5 %` = bv(continuous_model1ResultsMaths$`2.5 %`)
continuous_model1ResultsMaths$`97.5 %` = bv(continuous_model1ResultsMaths$`97.5 %`)
continuous_model1ResultsMaths$p.value1= ifelse(continuous_model1ResultsMaths$p.value< .001, "<.001" , pv1(continuous_model1ResultsMaths$p.value))
continuous_model1ResultsMaths$coefficient = paste0(continuous_model1ResultsMaths$estimate, "[", continuous_model1ResultsMaths$`2.5 %`, ";", continuous_model1ResultsMaths$`97.5 %`, "]")
continuous_model1ResultsMaths$stars = add.significance.stars(continuous_model1ResultsMaths$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model1ResultsMaths$p1 = paste0(continuous_model1ResultsMaths$p.value1, "")
continuous_model1ResultsMaths$p = paste0("p", continuous_model1ResultsMaths$p1)
continuous_model1ResultsMaths$new_coef = paste0(continuous_model1ResultsMaths$coefficient, continuous_model1ResultsMaths$stars)  #combine coefficients and stars into column.

#model 2 for continuous outcome
continuous_model2ResultsMaths$estimate = bv(continuous_model2ResultsMaths$estimate) #no leading 0 
continuous_model2ResultsMaths$`2.5 %` = bv(continuous_model2ResultsMaths$`2.5 %`)
continuous_model2ResultsMaths$`97.5 %` = bv(continuous_model2ResultsMaths$`97.5 %`)
continuous_model2ResultsMaths$p.value1= ifelse(continuous_model2ResultsMaths$p.value< .001, "<.001" , pv1(continuous_model2ResultsMaths$p.value))
continuous_model2ResultsMaths$coefficient = paste0(continuous_model2ResultsMaths$estimate, "[", continuous_model2ResultsMaths$`2.5 %`, ";", continuous_model2ResultsMaths$`97.5 %`, "]")
continuous_model2ResultsMaths$stars = add.significance.stars(continuous_model2ResultsMaths$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model2ResultsMaths$p1 = paste0(continuous_model2ResultsMaths$p.value1, "")
continuous_model2ResultsMaths$p = paste0("p", continuous_model2ResultsMaths$p1)
continuous_model2ResultsMaths$new_coef = paste0(continuous_model2ResultsMaths$coefficient, continuous_model2ResultsMaths$stars)  #combine coefficients and stars into column.


#model 3 for continuous outcome
continuous_model3ResultsMaths$estimate = bv(continuous_model3ResultsMaths$estimate) #no leading 0 
continuous_model3ResultsMaths$`2.5 %` = bv(continuous_model3ResultsMaths$`2.5 %`)
continuous_model3ResultsMaths$`97.5 %` = bv(continuous_model3ResultsMaths$`97.5 %`)
continuous_model3ResultsMaths$p.value1= ifelse(continuous_model3ResultsMaths$p.value< .001, "<.001" , pv1(continuous_model3ResultsMaths$p.value))
continuous_model3ResultsMaths$coefficient = paste0(continuous_model3ResultsMaths$estimate, "[", continuous_model3ResultsMaths$`2.5 %`, ";", continuous_model3ResultsMaths$`97.5 %`, "]")
continuous_model3ResultsMaths$stars = add.significance.stars(continuous_model3ResultsMaths$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model3ResultsMaths$p1 = paste0(continuous_model3ResultsMaths$p.value1, "")
continuous_model3ResultsMaths$p = paste0("p", continuous_model3ResultsMaths$p1)
continuous_model3ResultsMaths$new_coef = paste0(continuous_model3ResultsMaths$coefficient, continuous_model3ResultsMaths$stars)  #combine coefficients and stars into column.


#science
#model 1 for continuous outcome
continuous_model1ResultsScience$estimate = bv(continuous_model1ResultsScience$estimate) #no leading 0 
continuous_model1ResultsScience$`2.5 %` = bv(continuous_model1ResultsScience$`2.5 %`)
continuous_model1ResultsScience$`97.5 %` = bv(continuous_model1ResultsScience$`97.5 %`)
continuous_model1ResultsScience$p.value1= ifelse(continuous_model1ResultsScience$p.value< .001, "<.001" , pv1(continuous_model1ResultsScience$p.value))
continuous_model1ResultsScience$coefficient = paste0(continuous_model1ResultsScience$estimate, "[", continuous_model1ResultsScience$`2.5 %`, ";", continuous_model1ResultsScience$`97.5 %`, "]")
continuous_model1ResultsScience$stars = add.significance.stars(continuous_model1ResultsScience$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model1ResultsScience$p1 = paste0(continuous_model1ResultsScience$p.value1, "")
continuous_model1ResultsScience$p = paste0("p", continuous_model1ResultsScience$p1)
continuous_model1ResultsScience$new_coef = paste0(continuous_model1ResultsScience$coefficient, continuous_model1ResultsScience$stars)  #combine coefficients and stars into column.

#model 2 for continuous outcome
continuous_model2ResultsScience$estimate = bv(continuous_model2ResultsScience$estimate) #no leading 0 
continuous_model2ResultsScience$`2.5 %` = bv(continuous_model2ResultsScience$`2.5 %`)
continuous_model2ResultsScience$`97.5 %` = bv(continuous_model2ResultsScience$`97.5 %`)
continuous_model2ResultsScience$p.value1= ifelse(continuous_model2ResultsScience$p.value< .001, "<.001" , pv1(continuous_model2ResultsScience$p.value))
continuous_model2ResultsScience$coefficient = paste0(continuous_model2ResultsScience$estimate, "[", continuous_model2ResultsScience$`2.5 %`, ";", continuous_model2ResultsScience$`97.5 %`, "]")
continuous_model2ResultsScience$stars = add.significance.stars(continuous_model2ResultsScience$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model2ResultsScience$p1 = paste0(continuous_model2ResultsScience$p.value1, "")
continuous_model2ResultsScience$p = paste0("p", continuous_model2ResultsScience$p1)
continuous_model2ResultsScience$new_coef = paste0(continuous_model2ResultsScience$coefficient, continuous_model2ResultsScience$stars)  #combine coefficients and stars into column.


#model 3 for continuous outcome
continuous_model3ResultsScience$estimate = bv(continuous_model3ResultsScience$estimate) #no leading 0 
continuous_model3ResultsScience$`2.5 %` = bv(continuous_model3ResultsScience$`2.5 %`)
continuous_model3ResultsScience$`97.5 %` = bv(continuous_model3ResultsScience$`97.5 %`)
continuous_model3ResultsScience$p.value1= ifelse(continuous_model3ResultsScience$p.value< .001, "<.001" , pv1(continuous_model3ResultsScience$p.value))
continuous_model3ResultsScience$coefficient = paste0(continuous_model3ResultsScience$estimate, "[", continuous_model3ResultsScience$`2.5 %`, ";", continuous_model3ResultsScience$`97.5 %`, "]")
continuous_model3ResultsScience$stars = add.significance.stars(continuous_model3ResultsScience$p.value, cutoffs=c(0.05, 0.01, 0.001))
continuous_model3ResultsScience$p1 = paste0(continuous_model3ResultsScience$p.value1, "")
continuous_model3ResultsScience$p = paste0("p", continuous_model3ResultsScience$p1)
continuous_model3ResultsScience$new_coef = paste0(continuous_model3ResultsScience$coefficient, continuous_model3ResultsScience$stars)  #combine coefficients and stars into column.

```

put together into a dataframe for table 
```{r}
#english 
continuous_model1ResultsEnglish = continuous_model1ResultsEnglish %>% select(term, new_coef, p)
continuous_model2ResultsEnglish = continuous_model2ResultsEnglish %>% select(term, new_coef, p)
continuous_model3ResultsEnglish = continuous_model3ResultsEnglish %>% select(term, new_coef, p)

continuous_model1ResultsEnglish$model1_b <- paste0(continuous_model1ResultsEnglish$new_coef,"\n", continuous_model1ResultsEnglish$p) 
continuous_model2ResultsEnglish$model2_b <- paste0(continuous_model2ResultsEnglish$new_coef,"\n", continuous_model2ResultsEnglish$p) 
continuous_model3ResultsEnglish$model3_b <- paste0(continuous_model3ResultsEnglish$new_coef,"\n", continuous_model3ResultsEnglish$p) 

continuous_model1ResultsEnglish = continuous_model1ResultsEnglish %>% select(term, model1_b) %>% 
  rename("model1_english" = model1_b)
continuous_model2ResultsEnglish = continuous_model2ResultsEnglish %>% select(term, model2_b)%>% 
  rename("model2_english" = model2_b)
continuous_model3ResultsEnglish = continuous_model3ResultsEnglish %>% select(term, model3_b)%>% 
  rename("model3_english" = model3_b)


#add column to make it the same length for all 3 models - needs to be as long as model 3 
continuous_model1ResultsEnglish = continuous_model1ResultsEnglish %>% add_row(term = "caregiver_vocabStandardised") %>% 
  add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model1_english =paste0(cont_model1R2English$est,"[", cont_model1R2English$`lo 95`, ";", cont_model1R2English$`hi 95`,"]"), .after = 39)
continuous_model2ResultsEnglish = continuous_model2ResultsEnglish %>% add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model2_english =paste0(cont_model2R2English$est,"[", cont_model2R2English$`lo 95`, ";", cont_model2R2English$`hi 95`,"]"), .after = 39)
continuous_model3ResultsEnglish = continuous_model3ResultsEnglish %>% 
  add_row(term = "R2", model3_english =paste0(cont_model3R2English$est,"[", cont_model3R2English$`lo 95`, ";", cont_model3R2English$`hi 95`,"]"), .after = 39)

continuous_outcomeResultsEnglish = cbind(continuous_model1ResultsEnglish, continuous_model2ResultsEnglish, continuous_model3ResultsEnglish)
continuous_outcomeResultsEnglish = continuous_outcomeResultsEnglish %>% select(!3 & !5)

continuous_outcomeResultsEnglish = continuous_outcomeResultsEnglish %>% add_row(term = "Sociodemographic confounders", .after = 1) %>% 
  add_row(term = "Caregiver vocabulary", .before = 39) %>% 
  add_row(term = "Cohort member vocabulary", .before  = 41)

#maths
continuous_model1ResultsMaths = continuous_model1ResultsMaths %>% select(term, new_coef, p)
continuous_model2ResultsMaths = continuous_model2ResultsMaths %>% select(term, new_coef, p)
continuous_model3ResultsMaths = continuous_model3ResultsMaths %>% select(term, new_coef, p)

continuous_model1ResultsMaths$model1_b <- paste0(continuous_model1ResultsMaths$new_coef,"\n", continuous_model1ResultsMaths$p) 
continuous_model2ResultsMaths$model2_b <- paste0(continuous_model2ResultsMaths$new_coef,"\n", continuous_model2ResultsMaths$p) 
continuous_model3ResultsMaths$model3_b <- paste0(continuous_model3ResultsMaths$new_coef,"\n", continuous_model3ResultsMaths$p) 

continuous_model1ResultsMaths = continuous_model1ResultsMaths %>% select(term, model1_b) %>% 
  rename("model1_maths" = model1_b)
continuous_model2ResultsMaths = continuous_model2ResultsMaths %>% select(term, model2_b) %>% 
  rename("model2_maths" = model2_b)
continuous_model3ResultsMaths = continuous_model3ResultsMaths %>% select(term, model3_b) %>% 
  rename("model3_maths" = model3_b)


#add column to make it the same length for all 3 models - needs to be as long as model 3 
continuous_model1ResultsMaths = continuous_model1ResultsMaths %>% add_row(term = "caregiver_vocabStandardised") %>% 
  add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model1_maths =paste0(cont_model1R2Maths$est,"[", cont_model1R2Maths$`lo 95`, ";", cont_model1R2Maths$`hi 95`,"]"), .after = 39)
continuous_model2ResultsMaths = continuous_model2ResultsMaths %>% add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model2_maths =paste0(cont_model2R2Maths$est,"[", cont_model2R2Maths$`lo 95`, ";", cont_model2R2Maths$`hi 95`,"]"), .after = 39)
continuous_model3ResultsMaths = continuous_model3ResultsMaths %>% 
  add_row(term = "R2", model3_maths =paste0(cont_model3R2Maths$est,"[", cont_model3R2Maths$`lo 95`, ";", cont_model3R2Maths$`hi 95`,"]"), .after = 39)

continuous_outcomeResultsMaths = cbind(continuous_model1ResultsMaths, continuous_model2ResultsMaths, continuous_model3ResultsMaths)
continuous_outcomeResultsMaths = continuous_outcomeResultsMaths %>% select(!3 & !5)

continuous_outcomeResultsMaths = continuous_outcomeResultsMaths %>% add_row(term = "Sociodemographic confounders", .after = 1) %>% 
  add_row(term = "Caregiver vocabulary", .before = 39) %>% 
  add_row(term = "Cohort member vocabulary", .before  = 41) %>% 
  rename("term_maths" = term)

#science
continuous_model1ResultsScience = continuous_model1ResultsScience %>% select(term, new_coef, p)
continuous_model2ResultsScience = continuous_model2ResultsScience %>% select(term, new_coef, p)
continuous_model3ResultsScience = continuous_model3ResultsScience %>% select(term, new_coef, p)

continuous_model1ResultsScience$model1_b <- paste0(continuous_model1ResultsScience$new_coef,"\n", continuous_model1ResultsScience$p) 
continuous_model2ResultsScience$model2_b <- paste0(continuous_model2ResultsScience$new_coef,"\n", continuous_model2ResultsScience$p) 
continuous_model3ResultsScience$model3_b <- paste0(continuous_model3ResultsScience$new_coef,"\n", continuous_model3ResultsScience$p) 

continuous_model1ResultsScience = continuous_model1ResultsScience %>% select(term, model1_b) %>% 
  rename("model1_science" = model1_b)
continuous_model2ResultsScience = continuous_model2ResultsScience %>% select(term, model2_b) %>% 
  rename("model2_science" = model2_b)
continuous_model3ResultsScience = continuous_model3ResultsScience %>% select(term, model3_b) %>% 
  rename("model3_science" = model3_b)


#add column to make it the same length for all 3 models - needs to be as long as model 3 
continuous_model1ResultsScience = continuous_model1ResultsScience %>% add_row(term = "caregiver_vocabStandardised") %>% 
  add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model1_science =paste0(cont_model1R2Science$est,"[", cont_model1R2Science$`lo 95`, ";", cont_model1R2Science$`hi 95`,"]"), .after = 39)
continuous_model2ResultsScience = continuous_model2ResultsScience %>% add_row(term = "age5_standardised") %>% 
  add_row(term = "R2", model2_science =paste0(cont_model2R2Science$est,"[", cont_model2R2Science$`lo 95`, ";", cont_model2R2Science$`hi 95`,"]"), .after = 39)
continuous_model3ResultsScience = continuous_model3ResultsScience %>% 
  add_row(term = "R2", model3_science =paste0(cont_model3R2Science$est,"[", cont_model3R2Science$`lo 95`, ";", cont_model3R2Science$`hi 95`,"]"), .after = 39)

continuous_outcomeResultsScience = cbind(continuous_model1ResultsScience, continuous_model2ResultsScience, continuous_model3ResultsScience)
continuous_outcomeResultsScience = continuous_outcomeResultsScience %>% select(!3 & !5)

continuous_outcomeResultsScience = continuous_outcomeResultsScience %>% add_row(term = "Sociodemographic confounders", .after = 1) %>% 
  add_row(term = "Caregiver vocabulary", .before = 39) %>% 
  add_row(term = "Cohort member vocabulary", .before  = 41) %>% 
  rename("term_science" = term)

#put into one dataframe
regression_resultsTable = cbind(continuous_outcomeResultsEnglish, continuous_outcomeResultsMaths, continuous_outcomeResultsScience)
regression_resultsTable [is.na(regression_resultsTable )] <- "  "
regression_resultsTable = regression_resultsTable %>% select(!5) %>% 
  select(!8) %>% 
    slice(-(1)) %>% #remove intercept row
  add_row(term = "sex1", .after = 1) %>% #add in reference categories for factor variables
  add_row(term = "ethnicity1", .after = 3) %>% 
  add_row(term = "EAL1", .after = 9) %>% 
  add_row(term = "country1", .after =  12) %>% 
  add_row(term = "highest_nvq1", .after = 16) %>% 
  add_row(term = "oecd_income1", .after = 22) %>% 
  add_row(term = "occupational_status2", .after = 27) %>% 
  add_row(term = "wealth_quintiles1", .after = 31) %>% 
  add_row(term = "imd1", .after = 36 )
regression_resultsTable [is.na(regression_resultsTable )] <- "REFERENCE"

regression_resultsTable$term <- c("Sociodemographic confounders", "Sex (male)", "Sex (female)", 
                                  "Ethnicity \n (White)", "Ethnicity \n (mixed)", "Ethnicity \n (Indian)", "Ethnicity \n (Pakistani & Bangladeshi)", "Ethnicity \n (Black/ Black British)", "Ethnicity \n (other incl. Chinese)", 
                                  "EAL \n (English only)", "EAL \n (English and another language)", "EAL \n (only another language)", 
                                  "Country \n (England)", "Country \n (Wales)", "Country \n (Scotland)", "Country \n (Northern Ireland)",
                                  "Parent Education \n (NVQ1)", "Parent Education \n (None of these/overseas qualifications)", "Parent Education \n (NVQ2)", "Parent Education \n (NVQ3)", "Parent Education \n (NVQ4)", "Parent Education \n (NVQ5)", 
                           "Income Quintile 1", "Income Quintile 2", "Income Quintile 3", "Income Quintile 4", "Income Quintile 5", 
                           "Occupational Status \n (routine)", "Occupational Status \n (unemployed)", "Occupational Status \n (intermediate)", "Occupational Status \n (higher managerial)",  
                           "Wealth Quintile 1", "Wealth Quintile 2", "Wealth Quintile 3", "Wealth Quintile 4", "Wealth Quintile 5",
                          "Relative Neighbourhood \n Deprivation \n (most deprived decile)", "Relative Neighbourhood \n Deprivation \n (10 - <20%)", "Relative Neighbourhood \n Deprivation \n (20 - <30%)", "Relative Neighbourhood \n Deprivation \n (30 - <40%)", "Relative Neighbourhood \n Deprivation \n (40 - <50%)", "Relative Neighbourhood \n Deprivation \n (50 - <60%)", "Relative Neighbourhood \n Deprivation \n (60 - <70%)", "Relative Neighbourhood \n  Deprivation \n (70 - <80%)", "Relative Neighbourhood \n Deprivation \n (80 - <90%)", "Relative Neighbourhood \n Deprivation \n (least deprived decile)", "Caregiver Vocabulary", "Caregiver Vocabulary \n (Word Activity Test Score)", "Cohort Member Vocabulary", "Cohort Member Vocabulary \n (Naming Vocabulary Score)", "R2 (%)")
```


tanle with flextable package
```{r}
my_border = border= fp_border(color="black", width=1)
results_exploratory <- regression_resultsTable %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% #
  fontsize(size=10, part = "all") %>% #
  align(j=1, align="left", part="all") %>% 
  align(j=2:10, align="center", part="all") %>% 
  color(j=1:10, color="black", part="all") %>% 
  width(j=1, width=1) %>% 
  width(j=2:10, width=1.4) %>% 
  line_spacing(j=2:10, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:10, part="all", border=my_border) %>% 
  hline_bottom(j=1:10,part="body",  border=my_border) %>% 
  set_header_labels(term= "Variable", 
                    model1_english= "Model 1", model2_english= "Model 2",model3_english= "Model 3", 
                    model1_maths= "Model 1",model2_maths= "Model 2",model3_maths= "Model 3", 
                    model1_science= "Model 1",  model2_science= "Model 2",model3_science= "Model 3") %>% 
 add_header_row(values = c(" ", "English Outcome (B[95% CIs]", "Maths Outcome (B[95% CIs]", "Science Outcome (B[95% CIs]"), colwidths = c(1, 3, 3,3)) %>% 
  font(fontname = "Times New Roman", part="header") %>% 
  align(align="center", part="header") %>% 
  hline_top(j = 2:10, part = "all", border = my_border) %>% 
  bold(j = 1, i = c(1,47, 49), bold = TRUE) %>% 
  italic(j = 1, i = c(1,47, 49), italic = TRUE) %>% 
  add_header_lines(values = c("Table S9: Predicting Educational Attainment in English, Maths and Science (N=15,474)"))
 
 print(results_exploratory, preview = "docx")  
  
```

